%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Researcher \& Software Engineer} % Job title
    {TUBITAK BILGEM Cloud Computing Lab.} % Organization
    {Kocaeli, Turkey} % Location
    {Jan. 2022 - now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gained experience in system administrator role in Ubuntu / Debian based operating systems.}
        \item {Gained experience in networking, writing netplan configurations.}
        \item {Gained experience in various technologies such as Ansible, Docker, and Kubernetes and took part in various tasks using these tools.}
        \item {Implemented RESTFul API server with Gin framework in Go for Blockchain as a Service project.}
        \item {Gained experience in frameworks such as Gin framework in Golang, and FastAPI in Python in order to implement RESTful API.}
        \item {Gained experience in ORM libraries such as Gorm in Golang, and SQLalchemy in Python.}
        \item {Gained experience in some technologies such as OpenStack, OpenStack-ansible. And moreover, he worked on how to deploy an OpenStack, and how to automate it.}
        \item {Gained experience in Aptly \& Devpi in order to install Ubuntu/Debian and Python packages offline.}
        \item {Gained experience in LXC containers.}
        \item {Gained experience with Kubernetes client.}
        \item {Gained experience with SQL and NoSQL databases such as MySQL, PostgreSQL, and MongoDB.}
        \item {Implemented a Desktop application with Flutter in Dart.}
        \item {Used Atlassian products like Jira, Confluence and Bitbucket.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {Berqnet Firewall (Logo Cyber Security)} % Organization
    {Kocaeli, Turkey} % Location
    {Jul. 2021 - Exp. Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Some knowledge has been gained in the context of networking fundamentals.}
        \item {He took part in the DevOps project. In this project, the build and test system on a FreeBSD system was automated using Jenkins pipelines.}
        \item {Intermediate level Linux, Docker, Jenkins, Ansible, Vagrant and KVM/Qemu/Libvirt knowledge has been gained. Test Automation System has been applied using KVM/Qemu \& Jenkins \& Bash/Shell scripts.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
