%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Go \& Kubernetes \& RESTFUL API \& UI} % Job title
    {Blockchain as a Service} % Organization
    { } % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This project is about deploying blockchain nodes as "As a service". On the backend, there is a Restful API written in Golang that communicates with the Kubernetes client.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Flutter \& Ansible \& Bash Scripts} % Job title
    {OpenStack Installation Desktop App} % Organization
    { } % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The project provides a desktop application (Linux \& Mac \& Windows) in order to install OpenStack. It uses Ansible playbooks \& Bash scripts. Written with Flutter.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Ansible \& Bash Scripts \& Automation} % Job title
    {Ansible DevStack} % Organization
    { } % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The project provides an automated way to install DevStack, it includes several choices and plugins to install a DevStack}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Jenkins \& Docker \& Bash Scripts \& Libvirt \& Vagrant} % Job title
    {DevOps Project} % Organization
    { } % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {It is the project to automate the build and
        automation system. It uses bash scripts \& jenkins \& docker \&
        libvirt(kvm) and vagrant.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduation Project \& Mobile} % Job title
    {Personal Firewall for Android} % Organization
    { } % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {It restricts and shows the
        access of applications. The application is implemented with
        Flutter (VPNService is implemented with Java\&Kotlin for
        android side) (Graduation Project-1)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NodeJS \& ExpressJS \& HTML \& CSS \& Website} % Job title
    {GTU Rover Team Website} % Organization
    { } % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {It is the website for Rover Team
        of our university team. (rover.gtu.edu.tr)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Flutter \& Mobile} % Job title
    {Flutter Hackathon App and Bakery App} % Organization
    { } % Location
    { } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gained experience in various technologies such as Jenkins, Ansible, Docker, and Kubernetes and took part in various tasks using these tools.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
